A Decision Procedure for String Constraints with String-Integer Conversion and Flat Regular Constraints

### 2021-05-15 FMCAD2021/1_intro.tex

In \cite{Semenov84}, Semen\"{o}v just proved the decidability and did not provide an explicit decision procedure. So, in  \cite{Point86}, Point presented a first decision procedure for the satisfiability of $\paexp$ in a mathematical way, which is difficult to understand and therefore no implementation available based on which up to now to the best of our knowledge. So, another contribution of this paper is that we present a more understandable algorithm for $\paexp$'s satisfiability in a computational way and its prototypical implementation. Although the general framework of our algorithm is quite similar to Point's,  it contains the following improvements and corrections: 
   The syntax of Presburger arithmetic with exponential functions (denoted by $\paexp$) in our setting is more natural and easy to understand; Point's algorithm needs to transform the formula into DNF (disjunction normal form) before  eliminating any variables. In contrast, our algorithm just assumes that formulas are NNF (negation normal form). Therefore, our algorithm is much easy to follow and more efficient; Additionally, a sub-case of eliminating exponential terms in Point's algorithm is incorrect, we correct it by Lemma \ref{lem:exp-ineq} ( see later).

>>>>

In \cite{Semenov84}, Semen\"{o}v just proved the decidability and did not provide an explicit decision procedure. So, in  \cite{Point86}, Point presented a first decision procedure for the satisfiability of $\paexp$ in a mathematical way, which is difficult to understand and therefore no implementation available based on which up to now to the best of our knowledge. So, another contribution of this paper is that we present a more understandable algorithm for $\paexp$'s satisfiability in a computational way and its prototypical implementation. Although the general framework of our algorithm is quite similar to Point's,  it contains the following improvements and corrections: 
   The syntax of Presburger arithmetic with exponential functions (denoted by $\paexp$) in our setting is more natural and easy to understand; Point's algorithm needs to transform the formula into DNF (disjunction normal form) before  eliminating any variables. In contrast, our algorithm just assumes that formulas are NNF (negation normal form). Therefore, our algorithm is much easy to follow and more efficient; Additionally, a sub-case of eliminating exponential terms in Point's algorithm is incorrect, we correct it by Lemma \ref{lem:exp-ineq} (see later).
